\subsection{Mini Project A}
\label{sec:ProjA}

\subsection{Overview}
Your objective for Mini Project A is to design an environment logger. Add something about loggers in the environment, why the raspberry pi is usefult for this, etc.

\subsection{Pre-Project Requirements}
You will need to have completed all the previous practicals in order to complete this project.

\subsection{Outcomes}
In addition to creating a working system, you will learn about the following in this project:
\begin{itemize}
    \item ADCs
\end{itemize}

\subsection{Deliverables}
At the end of this practical, you must:
\begin{itemize}
    \item Demonstrate your working implementation to a tutor
    \item Submit your report to Vula
\end{itemize}

\subsection{Hardware Required}
\begin{itemize}
    \item All hardware from previous pracs
    \item 1 x Potentiometer
    \item 1 x LDR
    \item 1 x Temperature sensor (MCP9700A)
    \item ADC (MCP3008)
\end{itemize}


\subsection{Walkthrough}
\textbf{Instructions to tutors:}
\begin{itemize}
    \item Complete the project and draw up suitable instructions
    \item Come up with a demonstration rubric and report rubric (look at last year's project)
    \item The system should start on boot
    \item The system should have hardcoded thresholds. When a value goes over a threshold, an alarm should sound. A button must be pressed to dismiss the alarm.
    \item By default, the system continuously monitors the sensors every 500ms using this format:
    \begin{table}[H]
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
    RTC Time & System Timer & Pot   & Temp & Light \\ \hline
    10:17:15 & 00:00:00     & 0.5 V & 25 C & 10 \% \\ \hline
    10:17:20 & 00:00:05     & 1.5 V & 25 C & 15 \% \\ \hline
    \end{tabular}
    \end{table}
    \item The reset switch resets the timer and clean the console
    \item The frequency switch changes the frequency of the monitoring. The possible frequencies are 500ms, 1s, 2s. The frequency must loop between those values per event occurrence.
    \item The stop switch stops or starts the monitoring of the sensors. The timer is not affected by this functionality.
    \item The display switch displays the first five reading since the stop switch was pressed.
\end{itemize}
